FoRTE baseline

### 2019-07-09 analysis/paper/paper.Rmd
A few more notes on the multiple scatter model

- $\omega$ -- Clumping factor
- $LAI$ -- Leaf area index
- TAI -- Total area index (leaf and woody area)
- $LAI_e$ / $TAI_e$ -- "Effective" area indices (accounting for clumping)

@@

@@

@@

@@

Projected area, based on coefficients $\phi_1$ and $\phi_2$.

@@

>>>>

- $\omega$ -- Clumping factor
- $LAI$ -- Leaf area index
- $TAI$ -- Total area index (leaf and woody area)
- $LAI_e$ / $TAI_e$ -- "Effective" area indices (accounting for clumping)

@@

Effective LAI is just true LAI x clumping.

@@

Total area index (TAI) is leaf (LAI) + wood (WAI) area.

@@

Local exposed total area index ($TAI_l$) is the total area index divided by crown area index ($CAI$).

@@

Projected area ($a_{proj}$), based on coefficients $\phi_1$ and $\phi_2$.

@@

Optical depth ($\lambda$) is projected area over optical depth ($\mu$)

Transmittance for direct radiation of a canopy layer ($\tau_{beam}$) is:

$$ \tau_{beam} = (1 - CAI) + CAI exp\left( -\lambda TAI_l \right) $$

Transmittance for diffuse radiation of a canopy layer ($\tau_{diff}$):

$$ ext_1 = \phi_1 \TAI_l $$
$$ ext_2 = \phi_2 \TAI_l $$
$$ \tau_{diff} = (1 - CAI) - CAI exp\left( -ext_1 - ext_2 \right) ext_1^2 e^{exp_1} E_i(-exp_1) + (ext_1 - 1)$$

where $E_i$ is the exponential integral.

Backscatter for
